---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# narsscrapr

<!-- badges: start -->
[![lifecycle](https://img.shields.io/badge/lifecycle-experimental-brightgreen.svg)](https://www.tidyverse.org/lifecycle/#experimental)
<!-- badges: end -->

The goal of narsscrapr is to provide an interface to data collected by the [National Aquatic Resource Surveys (NARS)](https://www.epa.gov/national-aquatic-resource-surveys). 
    
Surveys conducted by NARS include: 

* [National Coastal Condition Assessment (NCCA)](https://www.epa.gov/national-aquatic-resource-surveys/ncca)
* [National Lakes Assessment (NLA)](https://www.epa.gov/national-aquatic-resource-surveys/nla)
* [National Rivers and Streams Assessment (NRSA)](https://www.epa.gov/national-aquatic-resource-surveys/nrsa)
* [National Wetland Condition Assessment (NWCA)](https://www.epa.gov/national-aquatic-resource-surveys/nwca)

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("corysauve/narsscrapr")
```
## Basic Usage 

You can scrape NARS data by `survey`, survey `year`, and survey `parameter`:
```{r}
library(narsscrapr)

scrape_nars(survey = "NLA", year = 2007, parameter = "Profile")
```

Metadata for each `parameter` is selected with `type = "metadata"`:
```{r}
library(narsscrapr)

scrape_nars(survey = "NLA", year = 2007, parameter = "Profile", type = "metadata")
```

## Contributing 

I welcome any contributions or suggestions for improving this package! Please open an issue to do so. 

## License 

The narsscrapr package is licensed under the MIT License. Please see the [LICENSE](LICENSE.md) for more details.
